### 2021-10-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@329cfc0d89a50bb36d3f53610c8391098ced00ae 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@270724f5f8d4bcdefa83ffa78999c0b39db71d61 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@f5113fb8e21a8251c011203c8810d2429ccb1546 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@4b6befa1ada7bcfaa54843b7c68ca41519463b35 🚀

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
using markdown and github actions}
\vskip 5em

%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}

\textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences

@@

@@

This document is for brainstorming the Colorado bumblebee metaweb
prediction project.

\hypertarget{data}{%
\section{1 Data}\label{data}}

The data consists of two parts, the field data collected at three
stations across Colorado, and the GBIF metaweb data aggregated and
cleaned by Julian R. and a student.

\hypertarget{field-data}{%
\subsection{1.1 Field data}\label{field-data}}

This data consists of nearly-daily records of visits between bee and
flower species for the months August-October. Data is collected from
three field sites: 1) Rocky Mountain Biological Lab (RMBL) 2) Niwot
Ridge 3) Pikes Peak

each with tens of plots each across an elevational gradient, collected
for 7/4/3 summers total.

\emph{To be determined}: specific number of plots per site and years per
site

\hypertarget{gbif-metaweb}{%
\subsection{1.2 GBIF metaweb}\label{gbif-metaweb}}

This data of a network of bee/flower species which have a record of both
occurring on GBIF for locations at some spatial grain

\emph{To be determined}: how does the scale of spatial aggregation
affect properties of metaweb, how much taxonomic overlap is there with
field data?---We have a lot of field data on interactions, but we can't
validate predictions on taxa that aren't present in field data. As a
result validation can only be done on interactions for which both
species appear in field data.

@@

@@

>>>>

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Forecasting the spatio-temporal uncoupling of
bumblebee-flower interaction networks}
\vskip 5em

%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{3,4,2}\quad %
Paul\,CaraDonna%
%
\,\textsuperscript{5,6,‡}\quad %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-6248-3007}{Philippe\,Desjardins-Proulx}%
%
\,\textsuperscript{3,2}\quad %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{3,2}\quad %
\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
%
\,\textsuperscript{4,2}\quad %
Jane E.\,Ogilvie%
%
\,\textsuperscript{5,‡}\quad %
\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
%
\,\textsuperscript{1,2}\quad %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{3,2,‡}\quad %
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{3,2,‡}\quad %
Julian\,Resasco%
%
\,\textsuperscript{7,‡}

\textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences\quad \textsuperscript{3}\,Université de
Montréal\quad \textsuperscript{4}\,Université de
Sherbrooke\quad \textsuperscript{5}\,Rocky Mountain Biological
Laboratory\quad \textsuperscript{6}\,Chicago Bontanic
Garden\quad \textsuperscript{7}\,University of Colorado Boulder

\textsuperscript{‡}\,These authors contributed equally to the work\\

@@

\emph{title ideas}: Forecasting the spatio-temporal uncoupling of
bumblebee-flower interaction networks

@@

Species interactions and climate change.

Two dimensions: spatial and temporal.

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Elevation gradients.
\end{enumerate}

\begin{itemize}
\tightlist
\item
  dispersal capacity and range shifts
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  Phenological uncoupling {[}cite{]}.
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Abundance is a function of time in the year
\end{itemize}

@@

\hypertarget{data}{%
\subsection{Data}\label{data}}

\hypertarget{models}{%
\subsection{Models}\label{models}}

We denote the predicted probability of two species, \(i\) and \(j\),
interacting a \(p_{ij}\). The outcome is here is to build a model \(f\),
or rather a set of candidate models, that take \(i\) and \(j\) and
inputs, and which potentially combine this with .features

\[p_{ij} = f(i,j)\]

\hypertarget{candidate-models}{%
\subsubsection{Candidate models}\label{candidate-models}}

\textbf{\emph{True Neutral}}:
\(f(i,j) = \frac{1}{\sum_i \sum_j 1} = 1 / (P\cdot F)\)

\textbf{\emph{Relative-abundance (interaction neutral)}}:
\(f(i,j) = A_i A_j\) where \(A_x\) is the relative abundance of species
\(x\).

\textbf{\emph{Relative-abundance + environment-embedding}}:
\(f(i,j) = g(i,j, E_i, E_j)\)

\textbf{\emph{Relative-abundance + phylogeny-embedding}}: \$\$

\textbf{\emph{Relative-abundance + environment-embedding +
phylogeny-embedding}}

\begin{figure}
\hypertarget{fig:concept}{%
\centering
\includegraphics{./figures/concept_v2.png}
\caption{todo}\label{fig:concept}
}
\end{figure}

In gravel et al 2017
\[P(X_{iy}, X_{jy}, L_{ijy} | E_y) = P(X_{iy},X_{jy}P(L_{ijy} | X_{iy}, X_{jy}, E_y)\]
Then decompose probability of co-occurence as
\[P(X_{iy}, X_{jy}) = P(X_{iy})P(X_{jy})\]

@@

\hypertarget{acknowledgements}{%
\subsection{Acknowledgements}\label{acknowledgements}}

### 2021-10-24 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@329cfc0d89a50bb36d3f53610c8391098ced00ae 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@270724f5f8d4bcdefa83ffa78999c0b39db71d61 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@f5113fb8e21a8251c011203c8810d2429ccb1546 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@4b6befa1ada7bcfaa54843b7c68ca41519463b35 🚀

\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
manuscripts using markdown and github actions}}}

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}
\vskip 1em
\textsuperscript{1}\,McGill University; \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences\\
\vskip 1em
\textbf{Correspondance to:}\\
Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\
}
\end{flushleft}

@@

\marginpar{\vskip 1em\flushright
{\small{\bfseries Keywords}:\par
pandoc\\pandoc-crossref\\github actions\\}
}

>>>>

\noindent {\LARGE \textbf{\textsf{Forecasting the spatio-temporal
uncoupling of bumblebee-flower interaction networks}}}

\medskip
\begin{flushleft}
{\small
%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}, %
\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
%
\,\textsuperscript{3,4,2}, %
Paul\,CaraDonna%
%
\,\textsuperscript{5,6,‡}, %
\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
%
\,\textsuperscript{1,2}, %
\href{https://orcid.org/0000-0002-6248-3007}{Philippe\,Desjardins-Proulx}%
%
\,\textsuperscript{3,2}, %
\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
%
\,\textsuperscript{3,2}, %
\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
%
\,\textsuperscript{1,2}, %
\href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
%
\,\textsuperscript{4,2}, %
Jane E.\,Ogilvie%
%
\,\textsuperscript{5,‡}, %
\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
%
\,\textsuperscript{1,2}, %
\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
%
\,\textsuperscript{3,2,‡}, %
\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
%
\,\textsuperscript{3,2,‡}, %
Julian\,Resasco%
%
\,\textsuperscript{7,‡}
\vskip 1em
\textsuperscript{1}\,McGill University; \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences; \textsuperscript{3}\,Université de
Montréal; \textsuperscript{4}\,Université de
Sherbrooke; \textsuperscript{5}\,Rocky Mountain Biological
Laboratory; \textsuperscript{6}\,Chicago Bontanic
Garden; \textsuperscript{7}\,University of Colorado Boulder\\
\textsuperscript{‡}\,These authors contributed equally to the work\\
\vskip 1em
\textbf{Correspondance to:}\\
Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\
}
\end{flushleft}

@@

\marginpar{\vskip 1em\flushright
{\small{\bfseries Keywords}:\par
species interactions\\ecological
forecasting\\pollinators\\bumbleebees\\network ecology\\}
}
